---
title: "Screen Scape TV Stations"
author: "Earl F Glynn<br><small>watchdoglab.substack.com/</small>"
date: "<small>`r Sys.Date()`</small>"
output:
  html_document:
    code_download: true
    theme: cerulean
    toc: yes
    toc_depth:  3
    toc_float:
      collapsed:  yes
      smooth_scroll: yes
    number_sections: yes
    code_folding:  show
---

Wikipedia Source:

* [List of television stations in the United States by call sign (initial letter K)](https://en.wikipedia.org/wiki/List_of_television_stations_in_the_United_States_by_call_sign_(initial_letter_K)
)

* [List of television stations in the United States by call sign (initial letter W)](https://en.wikipedia.org/wiki/List_of_television_stations_in_the_United_States_by_call_sign_(initial_letter_W)
)

```{r setup, echo = FALSE}
# http://biostat.mc.vanderbilt.edu/wiki/Main/KnitrHtmlTemplate
require(Hmisc)    # provides knitrSet and other functions
knitrSet(lang = 'markdown',   # If using blogdown: knitrSet(lang='blogdown')
         fig.align = 'left',
         w = 6.5,
         h = 4.5,
         cache = FALSE)
```

`r hidingTOC(buttonLabel = "Outline")`

```{r startYourEngines, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = NA)

time.1 <- Sys.time()
```

# Setup {.tabset .tabset-fade .tabset-pills}

## {.active}

## Packages

```{r}
library(rvest)
```

```{r Packages}
library(tidyverse)
```

Display formatting

```{r Display}
library(kableExtra)  # kable_styling
#library(IRdisplay)   # display_html (needed in Jupyter notebooks)
```

I/O

```{r IO}
library(readxl)      # read_xlsx
library(readr)       # write_csv
library(writexl)     # write_xlsx
```

 Graphics

```{r Graphics}
library(scales)      # comma, comma_format
```

## ggplot theme

[ggplot Themes Gallery](https://www.datanovia.com/en/blog/ggplot-themes-gallery/)

```{r ggplotTheme}
theme_set(theme_minimal() +

          theme(axis.text             = element_text(size = 10),
                axis.title            = element_text(size = 14),

                legend.position       = "bottom",

                plot.caption          = element_text(hjust = c(0.0,1.0),
                                                     size = 10),
                plot.caption.position = "plot",

                plot.title.position   = "plot",

                strip.background      = element_rect(fill = "aliceblue"),
                strip.text            = element_text(size = 14),

                title                 = element_text(size = 14)))

COLOR_BAR     <- "skyblue"
COLOR_OUTLINE <- "grey80"
```

## Helper functions

```{r Helpers}
Show <- function(data, caption="", bigMark="",
                 height = NULL, width = NULL, ...)
{
  data                                       %>%
  kable("html", caption=caption,
        format.args=list(big.mark=bigMark))  %>%
  kable_styling(bootstrap_options=c("striped", "bordered", "condensed"),
                position="left",
                full_width=FALSE, ...)       %>%
  scroll_box(height = height, width = width) #  %>%
# as.character()                             %>%      # Jupyter Only
# display_html()                                      # Jupyter Only
}
```

# TV Stations

## "K" stations

```{r}
kURL <- "https://en.wikipedia.org/wiki/List_of_television_stations_in_the_United_States_by_call_sign_(initial_letter_K)"
kPage <- read_html(kURL)
kTable <- html_table(kPage)
kTable <- kTable[[1]]
glimpse(kTable)
```
## "W" stations

```{r}
wURL <- "https://en.wikipedia.org/wiki/List_of_television_stations_in_the_United_States_by_call_sign_(initial_letter_W)"
wPage <- read_html(wURL)
wTable <- html_table(wPage)
wTable <- wTable[[1]]
glimpse(wTable)
```                        

```{r}
stations <-
  bind_rows(kTable, wTable)                                    |>
  separate(`City of license`, c("City", "State"), sep = ", ")  |>
  rename(
           Channel = 4,
           Network = 5
        )            
dim(stations)
```
```{r}
glimpse(stations)
```

```{r}
table(stations$State, useNA = "ifany")
```

Verify missing states are in California.

```{r}
stations |> filter(is.na(State)) |> Show()
```

Remove periods from D.C. and U.S.V.I.

```{r}
stations <- 
  stations  |>
  replace_na(list(State = "California")) |>
  mutate(State = 
           recode(State,
                  "D.C."     = "DC",
                  "U.S.V.I." = "VI"))   |>
  arrange(State, City)
```
 
# Save file

```{r}
write_xlsx(stations, paste0("US-TV-Statations-", format(time.1, "%Y-%m-%d"), ".xlsx"))
```


# Epilog {.tabset .tabset-fade .tabset-pills}

## {.active}

## Session Info

```{r devtoolsSessionInfo}
devtools::session_info()
```

</div>

```{r epilogDeltaTime, echo=FALSE}
time.2 <- Sys.time()
processingTime <- paste("Processing time:", sprintf("%.1f",
                        as.numeric(difftime(time.2,
                                            time.1, units="secs"))), "secs\n")
```

`r processingTime`
`r format(time.2, "%Y-%m-%d %H%M")`

